---
output: rmarkdown::github_document
---
![stability-wip](https://img.shields.io/badge/stability-work_in_progress-lightgrey.svg)

# porc

Tools to Work with 'Snort' Rules, Logs and Data

## Description

'Snort' is an open source intrusion prevention system capable of real-time traffic analysis and packet logging. Tools are provided to work with 'Snort' rulesets, logs and other data associated with the platform. More information on 'Snort' can be found at <https://www.snort.org/>.

## What's Inside The Tin

The following functions are implemented:

- `read_rules`:	Parse in a file of snort rules into a data frame
- `rule_vars`:	Extract all the '$'-named variables from Snort rules
- `as_rule_df`:	Helper to class a Snort rules data frame properly

## Installation

```{r eval=FALSE}
devtools::install_github("hrbrmstr/porc")
```

```{r message=FALSE, warning=FALSE, error=FALSE, include=FALSE}
options(width=120)
```

## Usage

```{r message=FALSE, warning=FALSE, error=FALSE}
library(porc)
library(tidyverse)

# current verison
packageVersion("porc")
```

## Basic rule reading

```{r message=FALSE, warning=FALSE, error=FALSE}
rules <- read_rules(system.file("extdata", "emerging-telnet.rules", package="porc"))

glimpse(rules)

rule_vars(rules)

glimpse(rules$options[[1]])

rules$options[[1]]
```

## A slightly bigger example

Let's slurp in all the [Emerging Threats](https://rules.emergingthreats.net/) Snort feed rules.

Grabbed & unpacked from: <https://rules.emergingthreats.net/open/snort-edge/emerging.rules.tar.gz>.

```{r message=FALSE, warning=FALSE, error=FALSE, cache=TRUE}
list.files("rules/emerging-rules", "\\.rules$", full.names=TRUE) %>% 
  map_df(~{
    cat(crayon::green(.x), "\n", sep="")
    x <- read_rules(.x)
    if (!is.null(x)) mutate(x, fil = .x)
  }) %>% as_rule_df()-> xdf
```

```{r}
glimpse(xdf)

xdf
```

What are the most referenced URLs in Emerging Threats feed?

```{r message=FALSE, warning=FALSE, error=FALSE}
unnest(xdf) %>% 
  filter(option == "reference") %>% 
  filter(grepl("^url", value)) %>% 
  select(value) %>% 
  mutate(value = sub("^url,", "", value)) %>% 
  count(value, sort=TRUE)
```

## Code of Conduct

Please note that this project is released with a [Contributor Code of Conduct](CONDUCT.md). By participating in this project you agree to abide by its terms.